Coherent FFL Type 1
========================================================

# Step Response Function

```{r}
step_response <- function(times,step) {
  response <- ifelse( times < 0 , 0 , step )
  return(response)
}

times = c(-0.5,0,0.5,1,1.5,2,2.5)
step = 1

steps = step_response(times,step)
data = cbind.data.frame(times,steps)
```

## Entire Plot for step repsonse

```{r fig.width=7, fig.height=6}
plot(times,steps,type="s", xlim= c(-0.5,2.5), ylim = c(0,1),xlab="time", ylab="Sx")
```



```{r, engine='bash'}
ffmpeg -framerate 10 -i %04dplot.png  -c:v libx264 -profile:v high -crf 20 -pix_fmt yuv420p  movie.mp4
```


# Step response FFL Y
## Yst = production / degrdation rates
```{r}

x  <- ifelse( times < 0 , 0 , -1 )

Yst <- function(times,x_active) {
  ## Y(t) = Yst(1-exp(-ay*t))
  
  y = x * (1- exp((-1 * times))) 
  return(y)
}


times = c(-0.5,0,0.5,1,1.5,2,2.5)
step = 1

ysteps = Yst(times,x)
```

## Entire Plot for step repsonse

```{r fig.width=7, fig.height=6}
plot(times,ysteps,type="l", xlim= c(-0.5,2.5),xlab="time", ylab="Sx")
```

# Step response FFL Z
## Yst = production / degrdation rates
```{r}
Zst <- function(times, y_levels) {
  ## Z(t) = Zst(1-exp(-a*t))
  y_active = ifelse( y_levels < 0.49 , 0 , 1 )
  y = y_active * y_levels
  z = y * (1- exp((-1 * times))) 
  return(z)
}

zsteps = Zst(times,ysteps)
```

## Entire Plot for step repsonse

```{r fig.width=7, fig.height=6}
plot(times,zsteps,type="l", xlim= c(-0.5,2.5),xlab="time", ylab="Z")
```



```{r}
setwd('~/Documents/R/FFL/images/')

frames = 16
times = seq(-0.5,2.5, by=.2)
###shift_times = seq(-01.1,2, by=.2)

for(i in 1:frames){
 # creating a name for each plot file with leading zeros
 if (i < 10) {name = paste('000',i,'plot.png',sep='')}

 if (i < 100 && i >= 10) {name = paste('00',i,'plot.png', sep='')}
 if (i >= 100) {name = paste('0', i,'plot.png', sep='')}
 new_times = seq(-0.5,times[i], by=.2)
 #shift_ntimes = seq(-01.1,shift_times[i], by=.2)
 #length(shift_ntimes)
 xsteps = step_response(new_times,1)
 ysteps = Yst(new_times,xsteps)
 zsteps = Zst(new_times,ysteps)
 length(zsteps)
 #saves the plot as a .png file in the working directory
 png(name)
 par(mfrow=c(3,1)) 
 plot(new_times,xsteps,type="s", xlim= c(-0.5,2.5), ylim = c(0,1),xlab="time", ylab="Sx")
 plot(new_times,ysteps,type="l", xlim= c(-0.5,2.5), ylim = c(0,1),xlab="time", ylab="Y")
 plot(new_times,zsteps,type="l", xlim= c(-0.5,2.5), ylim = c(0,1),xlab="time", ylab="Z")
 dev.off()
}
```

Coherent FFL type 1 OFF
========================================================





```{r, engine='bash'}
ffmpeg -framerate 10 -i %04dplot.png  -c:v libx264 -profile:v high -crf 20 -pix_fmt yuv420p  movie.mp4
```


# cherent type 1
## Yst = production / degrdation rates
```{r}
times = c(-0.5,0,0.5,1,1.5,2,2.5)
xon = ifelse( times < 0 , 0 , 1 )
xoff  <- ifelse( times <= 0 , 1 , 0 )

Yst <- function(times,x) {
  ## Y(t) = Yst(1-exp(-ay*t))
  y = x * (1- exp((-1 * times))) 
  return(y)
}
y = Yst(times,xon)

yneg= (y * -1) + 1
```

## Entire Plot for step repsonse

```{r fig.width=7, fig.height=6}
plot(times,ysteps,type="l", xlim= c(-0.5,2.5),xlab="time", ylab="Sx")
```

# Step response FFL Z
## Yst = production / degrdation rates
```{r}

zx = y
z = ifelse( y < 0.5 , y , yneg )
```

## Entire Plot for step repsonse

```{r fig.width=7, fig.height=6}
plot(times,z,type="l",xlab="time", ylab="Z")
```



```{r}
setwd('~/Documents/R/FFL/images/I1')

frames = 16
times = seq(-0.5,2.5, by=.2)
###shift_times = seq(-01.1,2, by=.2)

for(i in 1:frames){
 # creating a name for each plot file with leading zeros
 if (i < 10) {name = paste('000',i,'plot.png',sep='')}

 if (i < 100 && i >= 10) {name = paste('00',i,'plot.png', sep='')}
 if (i >= 100) {name = paste('0', i,'plot.png', sep='')}
 new_times = seq(-0.5,times[i], by=.2)
 #shift_ntimes = seq(-01.1,shift_times[i], by=.2)
 #length(shift_ntimes)
 xsteps = step_response(new_times,1)
 xsteps
 ysteps = Yst(new_times,xsteps)
 yneg = (ysteps * -1) + 1
 zsteps = ifelse( ysteps < 0.5 , ysteps , yneg )
 length(zsteps)
 #saves the plot as a .png file in the working directory
 png(name)
 par(mfrow=c(3,1)) 
 plot(new_times,xsteps,type="s", xlim= c(-0.5,2.5), ylim = c(0,1),xlab="time", ylab="Sx")
 plot(new_times,ysteps,type="l", xlim= c(-0.5,2.5), ylim = c(0,1),xlab="time", ylab="Y")
 plot(new_times,zsteps,type="l", xlim= c(-0.5,2.5), ylim = c(0,1),xlab="time", ylab="Z")
 dev.off()
}
```